An Abstraction-based Approach to Network Synthesis

### 2016-10-31 paper/abstraction/paper.tex
update section 3

\sysname achieves this by allowing the operator to abstract the network into 
a role-based topology that captures a class of concrete topologies and then write a 
routing specification over this abstraction. Figure~\ref{fig:example3} shows an example of one 
such abstraction for the datacenter networks. The network is partitioned into 5 different roles:
local tor (TL), global tor (TG), local aggregator (AL), global aggregator (AG), and spine (S).
Each router in the concrete topology maps to exactly one abstract role.

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.6\columnwidth]{figures/example3}
  \caption{Role-based abstraction for the datacenter in Figure~\ref{fig:example}.}
  \label{fig:example3}
  \vspace{-1em}
\end{figure}

Consider again the datacenter routing policy we wrote before. 
%
We will now rewrite the policy over the network abstraction shown in figure~\ref{fig:example3}.
This abstraction splits the network into 5 roles: local tor, global tor, local aggregator, global 
aggregator, and spine. Intuitively, each concrete router in the network must map to exactly one role.
Whenever there is a link between routers in the concrete network, there must be an associated link
between their abstract roles. Thus the role-based abstraction is an overapproximation of the connectivity
of the concrete network.

The new routing policy can only refer to locations in the abstract topology. We choose these 5 roles,
since its gives us fine enough granularity to implement our policy, but is general enough to enable 
expansion (\EG, by adding new concrete routers for a given role).

We can modify the concrete routing policy for this abstraction in the following way. First we change the Routing policy:
%
\begin{code}
\Define Routing =
    \{\$PG \Path \End(TG)
     \$PL \Path \End(TL)
     \True \Path \Exit(Peer1 \Prefer Peer2) \}
\end{code}
\noindent%

Here we introduce two prefix \emph{template} variables. The policy says that traffic for each 
global prefix associated with the template variable \$PG should end up at its corresponding 
destination router contained in the abstract TG role. The second line does something similar 
for all local prefixes. Finally, the last line remains the same as before.

Next we can modify the Locality constraint for the abstraction in a straightforward way:
%
\begin{code}
\Define Locality = \{\$PL \Path \Always(\In)\}
\end{code}
\noindent%

Finally, we can add the "valleyfree" constraint. We are able to encode this constraint for the
abstract topology because we have retained enough structure to understand what a valley is. 
%
\begin{code}
\Define Tor = \{TL,TG\}
\Define Agg = \{AL,AG\}
\Define Spn = \{S\}
\Define ValleyFree =
    \{\True \Path \Novalley(Tor,Agg,Spn)\}
\end{code}
\noindent%

The constraint prevents traffic from over taking a path that traverses 
either [Agg->Tor->Agg] or [Spn->Agg->Spn]. The final policy remains the same as before,
by combining each of these policies together.
%
\begin{code}
\Define Main = 
    Routing & 
    Locality & 
    ValleyFree & 
    \Agg(PG, \In -> \Out)
\end{code}
\noindent%

When \sysname compiles the above policy, it guarantees that the forwarding behavior 
of the network will be correct for any concrete instantiation of the abstract network,
and for any combination of failures that may occur in the concrete network.
Furthermore, if we want to expand our network for example by adding additional spine 
routers, \sysname will guarantee that the expansion will be incremental (\IE, only
configurations for routers local to the expansion will need to change).

>>>>

\sysname achieves this by allowing the operator to abstract the network into 
a role-based topology that captures a class of concrete topologies and then write a 
routing specification over this abstraction. Figure~\ref{fig:example3} shows an example of one 
such abstraction for the datacenter networks.

The network is partitioned into 5 different roles:
local tor (TL), global tor (TG), local aggregator (AL), global aggregator (AG), and spine (S).
Intuitively, each concrete router in the network must map to exactly one role.
Whenever there is a link between routers in the concrete network, there must be an associated link
between their abstract roles. Thus the role-based abstraction is an overapproximation of the connectivity
of the concrete network.

In order to refine the abstraction to capture more precisely the kinds of concrete networks of interest, 
we introduce a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
with a symbolic variable (\EG, $e1, e2, \ldots$) that denotes a constraint on the number of nodes/edges 
that may appear in any given concrete network. Operators can then add constraints to relate symbolic 
variables taken from any valid SMT theory. For example, in Figure~\ref{fig:example3}, the variable $e1$
represents the number of outgoing edges from any concrete node mapped to the TG role to other concrete
nodes mapped to the AG role. Similarly, we introduce a node multiplicity variable for each role. For example,
the multiplicity variable $AG$ represents the number of concrete nodes that map the the AG role. We can then 
add constraints over these symbolic variables to capture invariants in the concrete networks. For example, 
if we only want to consider networks where TG and AG routers form a full mesh in each pod we would add the
following constraints: $e1 = AG$, $e2 = TG$. \ryan{how to add the constraints to the image? in latex or powerpoint?}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.7\columnwidth]{figures/example3}
  \caption{Role-based abstraction for the datacenters in Figure~\ref{fig:example}.}
  \label{fig:example3}
  \vspace{-1em}
\end{figure}

Now let us configure the datacenter networks by writing a routing policy over the 
abstract topology. The first part of the policy will be:
%
\begin{code}
\Define Routing =
    \{\$PG \Path \End(TG)
     \$PL \Path \End(TL)
     \True \Path \Exit(Peer1 \Prefer Peer2)\}
\end{code}
\noindent%

This defines a group of constraints for the basic routing behavior. 
%
The first line introduces a prefix \emph{template} variable. It says that traffic for each 
global prefix associated with the template variable \$PG has the constraint that it should follow 
a path that ends at its corresponding destination router contained in the abstract TG role. 
The second line does the same thing for all local prefixes. 
The final rule matches all other
IP prefix destinations and allows traffic to follow a path that leaves the datacenter through either
of its peers (Peer1 or Peer2) with a preference for leaving through Peer1. The \Prefer~ symbol indicates
that traffic should satisfy the constraint on the left whenever possible, and only resort to the backup (right)
when this is not possible due to failures.%

Next we can capture the constraint that traffic for local prefixes must stay local to the datacenter.
We do this with the following \sysname code:
%
\begin{code}
\Define Locality = \{\$PL \Path \Always(\In)\}
\end{code}
\noindent%
%
The Locality constraint applies to any traffic destined for a local prefix and adds
the constraint that the traffic must follow a path that matches an internal location 
(\IE, a router inside the datacenter) at each hop of the path. This prevents traffic 
from ever entering from or leaving through an external peer. Finally, we can combine 
these constraints together as follows:

%
%Finally, we can add the "valleyfree" constraint. We are able to encode this constraint for the
%abstract topology because we have retained enough structure to understand what a valley is. 
%
%\begin{code}
%\Define Tor = \{TL,TG\}
%\Define Agg = \{AL,AG\}
%\Define Spn = \{S\}
%\Define ValleyFree =
%    \{\True \Path \Novalley(Tor,Agg,Spn)\}
%\end{code}
%\noindent%
%
%The constraint prevents traffic from over taking a path that traverses 
%either [Agg->Tor->Agg] or [Spn->Agg->Spn]. The final policy remains the same as before,
%by combining each of these policies together.
%
%
\begin{code}
\Define Main = Routing & Locality & \Agg(PG, \In -> \Out)
\end{code}
\noindent%

This defines the main policy as the conjunction of the Routing and Locality constraints. It 
also declares an additional constraint that we want to perform aggregation for global prefixes
by summarizing them into the more general prefix PG at the border of the datacenter
(\IE along any edge starting inside our datacenter and ending outside).

When \sysname compiles the above policy, it guarantees that the forwarding behavior 
of the network will be correct for any concrete instantiation of the abstract network,
and for any combination of failures that may occur in the concrete network.
Furthermore, \sysname will generate configurations in such a way that,
if we want to expand our network (\EG, by adding additional spine routers as in 
figure~\ref{fig:example2}), the expansion will be incremental (\IE, only
configurations for routers local to the expansion will need to change).

\subsection{Abstract Analysis}

Although \sysname can ensure correct forwarding behavior independent of the 
exact concrete topology or failure scenario, it is often useful to be able 
to ask "what if" questions. To this end, we develop sound analyses over the
abstract topology to answer questions about worst-case connectivity.
